Rough Draft

### 2017-11-13 Article submission/roughdraft.tex
edited results

Predictors with p-values less than 0.01 in univariate analysis, shown in table b, were included in the full Cox model for cross-validation. Average metrics for test and training sets are in table c. Although not impressively high, metrics did not change substantially from training to test set, indicating that the model does not overfit. Examining model parameters of the training models showed that the the average frequency of a question's tags had an extremely high coefficient (> 20). To address this, a square root transformation was applied. Restricted cubic splines were fit to continous predictors. A spline of five knots was fit to the number of characters in the user-defined device name. Splines of four knots were fit to the number of characters in a question's text, average number of characters in a question's tags, and the ratio of number of line breaks to the number of characters in a question's text. Results of cross-validation for the model including the splines are in table d. As refitting the model without insignificant predictors did not effect predictive performance, all variables were included. The final model, with all variables described above including splines, was fit to the full data.

>>>>

Predictors with p-values less than 0.01 in univariate analysis are shown in table b. The univariate model for the average frequency of a question's tags displayed an extrememly high hazard coefficient (33.8). To address this, a square root transformation was used on the variable, bringing the hazard coefficient to 4.2. Average performance metrics for the full model and its predictions for test and training sets, found in table c, were considerably low. However, metrics did not change substantially from training to test set, indicating that the model does not overfit. A spline of five knots was fit to the number of characters in the user-defined device name. Splines of four knots were fit to the number of characters in a question's text, average number of characters in a question's tags, and the ratio of number of line breaks to the number of characters in a question's text. Results of cross-validation for the model including the splines are in table d. As refitting the model without insignificant predictors did not effect predictive performance, all variables were included. The final model, with all variables described above including splines, was fit to the full data.
